\Large \bf Frontrunning

### 2018-07-03 frontrunning/Latex/sections/paper.tex
[frontrunning] frontrunning attacks on namespaces

 %Mahsa ToDos:%
New attacks:\par\noindent
Ghazal\par\noindent
%@mahsa: write on ghazal and namecoin but with the focus on ghazal front running applications
%@ possibility of PoC attack (@shayan @mahsa)
%===========================%

>>>>

%Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method) 
\subsubsection{Namespaces} Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Frontrunning can occur within other blockchain based applications such as naming systems. Blockchain-based namespaces have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduces single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, frontrunning attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can frontrun other user's \textit{registerdomain} at a good profit by paying higher transaction fees. In both cases the adversarial party could sell the domain name to the users for higher price.

%@ possibility of PoC attack (@shayan @mahsa)
%===========================%
